Adaptive Sequential Model Selection

### 2015-07-08 paper.tex
answered Rob's questions and replaced '[k]' notation with '1:k' (or '0:k' as appropriate)

More generically, we observe data $Y \in \cY$, with unknown sampling distribution $F$. We then use $Y$ to generate an adaptive sequence of $d$ nested models
\[
M_0(Y) \sub M_1(Y) \sub \cdots \sub M_d(Y) \sub M_\infty.
\]
\WFcomment{should probably end with $M_{d-1}(Y)$. need to fix this   throughout paper.}
\RTcomment{Will- be more specific here---   A parametric model  with specified nonzero support?}

By ``model,'' we mean a family of probability distributions for $Y$. Without loss of generality, we can take $M_\infty$ as the union of all models under consideration.

@@

First suppose that we have single step p-values for testing
\[
H_{k}:\; F\in M_{k-1}(Y)
\]
against the alternative that $F\in M_\infty\setminus M_{k-1}$. The $p$-values must account for the fact that the models are chosen adaptively. 
\citet{gsell2013sequential} and \citet{li2015accumulation} propose stopping rules that operate on the sequence $p_{[d]}$. These stopping rules provably control certain error rates, provided that the null $p$-values are mutually independent and independent of the non-null $p$-values. 
We review these methods in Section~\ref{sec:sequential} .

@@

Most of our examples will focus on the important and familiar problem of adaptively selecting a set of predictors in linear regression models. In this problem, we observe a random response $Y\in \R^n$ as well as a fixed design matrix $X\in \R^{n \times p}$, whose columns correspond to candidate predictors. For each {\em active set} $E \sub [p]$, there is a corresponding candidate model
\[
M(E):\; Y \sim \cN( X_E\beta, \sigma^2 I_n),
\]
which is a subset of the {\em full model}
\[
M_\infty:\; Y \sim \cN(X\beta, \sigma^2I_n).
\]
The error variance $\sigma^2$ may be known or unknown depending on the context. The complete sufficient statistic for $M(E)$ is $X_E'Y$ if $\sigma^2$ is known, or else $\left(X_E'Y, \|Y\|^2\right)$.

@@

The following proposition shows that~\eqref{eq:indepCond_random_k0} is the correct generalization of~\eqref{eq:indepCond_fixed_k0} to the random-hypothesis case.
\begin{proposition}
  Let $\hk$ be a stopping rule that operates on sequences
  $p_{[d]}(Y)$ of $p$-values for ordered hypotheses $H_{[d]}(Y)$. 
  For some function $g$, let 
  \[
  \Err(\hk,g) = \E\left[ g\left(\hk(Y), k_0(Y)\right)\right],
  \]

  Suppose that the rule $\hk$ controls $\Err$ at $\alpha$ under
  independence when $H_{[d]}$ are fixed. That is, suppose that
  whenever $H_{[d]}$ are fixed and $p_{[d]}$
  satisfy~\eqref{eq:indepCond_fixed_k0}, we have
  \[
  \Err(\hk, g) \leq \alpha
  \]

  Then, $\hk$ controls $\Err$ at $\alpha$
  whenever $p_{[d]}$ satisfy~\eqref{eq:indepCond_random_k0}.
\end{proposition}
\begin{proof}
  For any fixed $k_0$ and $q_1,\ldots, q_{k_0}$, we can construct a
  problem with $\tilde p_k \sim \delta_{q_k}$ for $k\leq k_0$ and 
  $\tilde p_k \sim \text{Unif}[0,1]$ for $k > k_0$. 
  \RTcomment{Will; what are the qk?  you mean we just choose and fix some values qk? Say so.}Then, for the
  fixed hypotheses 
  $\widetilde H_k:\; \tilde p_k \sim \text{Unif}[0,1]$, we have
  \[
  f(k_0, q_{[k_0]}) 
  = \E\left[ g\left(\hk(\tilde p_1, \ldots, \tilde p_d),
      k_0\right) \right],
  \]
  which is less than or equal to $\alpha$ by assumption.

  But then, by the condition~\eqref{eq:indepCond_random_k0}, we have
  \begin{align}
    \Err(\hk,g) &\;=\; \E\left[ \;\E\left[ g\left(\hk(p_1,\ldots, p_d), k_0(Y)\right) \; \mid \; k_0(Y), \; p_{[k_0]}(Y)\right] \; \right]\\
    &\;\leq\; \E\left[f(k_0, p_{[k_0]})\right] \;\leq\; \alpha.
  \end{align}
\end{proof}

@@

Sections~\ref{sec:pValsIndep}--\ref{sec:SSP} discuss conditions on the model sequence $M_{[d]}$ and the $p$-value sequence $p_{[d]}$ under which~\eqref{eq:stochLargeCond_random_k0} is satisfied.

@@

Consider any filtration
\[
\sF_0 \sub \sF_1 \sub \cdots \sub \sF_d
\]
for which $M_{[k]}$ is measurable with respect to $\sF_k$. We say that $\sF_{[d]}$ {\em separates} the $p$-values $p_{[d]}$ if 
\begin{enumerate}
\item $p_k(Y)$ is conservative given $\sF_{k-1}$ 
  when $F\in M_{k-1}(Y)$, and
\item $p_k(Y)$ is measurable with respect to $\sF_k$.
\end{enumerate}
If $p_k$ is exact, the first requirement is equivalent to requiring that $p_k$ is independent of $\sF_{k-1}$ on the event $F\in M_{k-1}(Y)$ (i.e., the event when $p_k$ is null).

@@

  Let $p_{[d]}$ be selective $p$-values for $M_{[d]}$, 
  separated by $\sF_{[d]}$.

@@

We will concern ourselves mainly with the {\em sufficient filtration} for the path $M_{[k]}$, defined as
\[
\sF_k^{\text{suff}} = \sF(M_{[k]}, T_k),
\]
\RTcomment{Will- define $M_{[k-1]}$..  it is  the collection $\{ M_1 M_2 \ldots M_{k-1}\}$?}
We will suppress the superscript and use $\sF_k$ to mean $\sF_k^{\text{suff}}$ for the remainder of the article.

The sufficient filtration separates $p_{[d]}$ if and only if 
\begin{enumerate}
\item $p_k$ is conservative given $M_{[k-1]}$ and $T_{k-1}$, and
\item $p_k$ is a function of $M_{[k]}$ and $T_k$.
\end{enumerate}

To be a valid selective $p$-value for a single step, $p_k$ only needs to be conservative conditional on $M_{k-1}$. In general, it is more stringent to additionally require that $p_k$ must also condition on $T_{k-1}$ as well as the entire subpath $M_{[k-1]}$. In most cases of interest, however, the ``extra'' conditioning is redundant, for two reasons.

First, most selective tests already condition on $T_{k-1}$ in order to eliminate nuisance parameters. Second, as we will show in Section~\ref{sec:SSP}, for most path algorithms of interest we have
\begin{equation}\label{eq:SSP}
\sF(M_k, \, T_k) = \sF(M_{[k]}, \, T_k).
\end{equation}
Thus, most single-step selective $p$-values we would contemplate using are already exact conditional on $\sF_{k-1}$.

@@

We say that a path algorithm $M_{[d]}(\cdot)$ satisfies the {\em subpath sufficiency principle} (SSP) if~\eqref{eq:SSP} holds for every $k$. Equation~\eqref{eq:SSP} means that if we know $M_k(Y) = M$, then we can compute the entire subpath of models $M_{[k]}$ knowing only $T(Y, \, M)$, the sufficient statistic of model $M$. For example, given that four steps of forward stepwise linear regression yield the active set $E_4 = \{1,5,7,11\}$, the order in which these variables were included can be determined from $T_4 = X_{E_4}'Y$.

@@

Equation~\eqref{eq:onlyT} shows that $j_1,\ldots, j_{k-1}$ all depend on $Y$ only through $T_k(Y)$. As a result, it also follows that the enitre sequence $M_{[k]}(Y)$ depends only on $T_k(Y)$.
\end{proof}

@@

Collecting together the threads of this section, we can arrive at our main result: a fairly general sufficient condition for a $p$-value sequence to be independent on nulls.
\begin{theorem}[Sufficient Condition for Independence on Nulls] \label{thm:suffCond}
Assume that $T(Y; M)$ is a complete sufficient statistic for each candidate model $M$, that $p_k$ are exact selective $p$-values for $M_{k-1}$, and that $M_{[d]}(\cdot)$ satisfies the SSP.

If $p_k$ is $\sF_k$-measurable for each $k$, then the $p$-value sequence $p_{[d]}(Y)$ is independent on nulls.
\end{theorem}

\begin{proof}
We apply the definition of completeness to the function 
\[
h(T(Y; \, M)) \;=\; 
\P(p_k(Y) \leq \alpha \mid T(Y; \, M), \, M_{k-1}(Y) = M) - \alpha
\]
If $p_k$ is exact given $M_{k-1} = M$, then 
\[
\E_F[h(T_{k-1}) \mid M_{k-1}=M] \;=\; 0
\] 
for every $F\in M$. Therefore, we must have $h(T_{k-1})\eqAS 0$, so $p_k$ is independent of $\sF(M_k, T_{k-1})$. Because $M_{[d]}$ satisfies the SSP, $p_k$ is also independent of $\sF_{k-1} = \sF(M_{[k-1]}, T_{k-1})$.

If $p_k$ is also $\sF_k$-measurable, then the sufficient filtration separates $p_{[d]}$, implying that $p_{[d]}$ is independent on nulls.
\end{proof}

@@

If we follow this strategy, then the reference distribution for $U(Y)$ is measurable with respect to $T_{k-1}$ and $M_{k-1}$; moreover, if $U(Y)$ is also measurable with respect to $(M_k, T_k)$, the next model in the path and its sufficient statistics, then $p_k$ is measurable with respect to $\sF_k$, and so the $p$-value sequence $p_{[d]}$ will be independent on nulls per Theorem~\ref{thm:suffCond}.

@@

\begin{theorem}
  Assume the model path $M_{[d]}$ is obtained by forward stepwise 
  linear regression. Then, for a candidate active set $E$ of size $k$, 
  the set $A = \{E_k = E, \;X_E'Y = u\}$ is characterized 
  exactly by the constraints $X_E'Y=u$ and
  \[
  v_j^-(E,u) < X_j'Y < v_j^+(E,u), \quad\forall j \notin E,
  \]
  for $v_j^-$ and $v_j^+$ given explicitly in
  Equations~(\ref{eq:vMinus_FS}--\ref{eq:vPlus_FS}).
  Thus, $A$ corresponds exactly to 
  a set with $2(p-k)$ linear inequality constraints and $k$
  linear equality constraints on $Y$.
\end{theorem}

@@

\begin{theorem}
  Assume that $M_\infty$ is an exponential family model
  of the form
  \[
  Y \sim \exp\{ \theta'U(y) - \psi(\theta) \}\,d\nu(y),
  \]
  with $\Theta \sub \R^p$ convex, and assume
  that the model path $M_{[d]}$ is given 
  by the ever-active set for the $\ell_1$-penalized problem
  \begin{equation}\label{eq:regProblem}
  \hat\theta^r = \argmin_{\theta\in \Theta} 
  -\ell(\theta) + \lambda_r\|\theta\|_1,
  \end{equation}
  for some sequence $\lambda_r > 0$.

@@

\WFcomment{Should we compute the FWER and FDR only conditional on screening? Strong / Forward / Basic should all be correct given screening since they condition on $p_{[k_0-1]}$.}

@@

Essentially, we will want to partition the information in $Y$ according to the filtration:
\begin{align}\nonumber
  \sF(M_0,T_0) &\underlabel_{\text{selection } 1} 
  \sF(M_{[1]},T_0) \underlabel_{\text{inference } 1}
  \sF(M_{[1]},T_1) \quad \sub \;\;\cdots\\[8pt]
  \label{eq:infoPartition}
  \cdots\;\; \sub \quad&
  \sF(M_{[d-1]},T_{d-1}) \underlabel_{\text{selection } d}
  \sF(M_{[d]},T_{d-1}) 
  \underlabel_{\text{inference } d}
  \sF(M_{[d]}, T_d)
\end{align}

@@

\begin{comment}
\WFcomment{There is a filtration interpretation when you have the appropriate sufficiency properties.} Let $\sF_{k,i}$ denote the $\sigma$-algebra generated by $M_{[k]}$ and $p_{[i]}$.
\begin{align*}
  \sF_{k,i} &= \sF(M_{[k]},p_{[i]})\\
  \sF_0 &\underlabel_{\text{selection } 1} \sF_{1,0} \underlabel_{\text{inference } 1}
  \sF_{1,1} \;\;\sub \cdots \sub\;\;
  \sF_{d-1,d-1} \underlabel_{\text{selection } d} \sF_{d,d-1}
  \underlabel_{\text{inference } d} \sF_{d,d}
\end{align*}
\end{comment}

>>>>

More generically, we observe data $Y \in \cY$, with unknown sampling distribution $F$. We then use $Y$ to generate an adaptive sequence of $d$ nested models
\[
M_0(Y) \sub M_1(Y) \sub \cdots \sub M_d(Y) \sub M_\infty.
\]
\WFcomment{should probably end with $M_{d-1}(Y)$. need to fix this throughout paper.}
\RTcomment{Will- be more specific here---   A parametric model  with
  specified nonzero support?}
\WFcomment{Not necessarily. As far as I can tell, there's no need to restrict ourselves in either case. $Y\sim U[0,\theta]$ is a perfectly good model; so is a Cox proportional hazards model.}

By ``model,'' we mean a family of probability distributions for $Y$. Without loss of generality, we can take $M_\infty$ as the union of all models under consideration. We will use the notation $M_{0:k}$ to denote the sequence of the first $k$ models.

@@

First suppose that we have single step p-values for testing
\[
H_{k}:\; F\in M_{k-1}(Y)
\]
against the alternative that $F\in M_\infty\setminus M_{k-1}$. The $p$-values must account for the fact that the models are chosen adaptively. 
\citet{gsell2013sequential} and \citet{li2015accumulation} propose stopping rules that operate on the sequence $p_{1:d}$. These stopping rules provably control certain error rates, provided that the null $p$-values are mutually independent and independent of the non-null $p$-values. 
We review these methods in Section~\ref{sec:sequential} .

@@

Most of our examples will focus on the important and familiar problem of adaptively selecting a set of predictors in linear regression models. In this problem, we observe a random response $Y\in \R^n$ as well as a fixed design matrix $X\in \R^{n \times p}$, whose columns correspond to candidate predictors. For each {\em active set} $E \sub \{1,\ldots,p\}$, there is a corresponding candidate model
\[
M(E):\; Y \sim \cN( X_E\beta, \sigma^2 I_n),
\]
which is a subset of the {\em full model}
\[
M_\infty:\; Y \sim \cN(X\beta, \sigma^2I_n).
\]
The error variance $\sigma^2$ may be known or unknown depending on the context. The complete sufficient statistic for $M(E)$ is $X_E'Y$ if $\sigma^2$ is known, or else $\left(X_E'Y, \|Y\|^2\right)$.

@@

The following proposition shows that~\eqref{eq:indepCond_random_k0} is the correct generalization of~\eqref{eq:indepCond_fixed_k0} to the random-hypothesis case.
\begin{proposition}
  Let $\hk$ be a stopping rule that operates on sequences
  $p_{1:d}(Y)$ of $p$-values for ordered hypotheses $H_{1:d}(Y)$. 
  For some function $g$, let 
  \[
  \Err(\hk,g) = \E\left[ g\left(\hk(Y), k_0(Y)\right)\right],
  \]

  Suppose that the rule $\hk$ controls $\Err$ at $\alpha$ under
  independence when $H_{1:d}$ are fixed. That is, suppose that
  whenever $H_{1:d}$ are fixed and $p_{1:d}$
  satisfy~\eqref{eq:indepCond_fixed_k0}, we have
  \[
  \Err(\hk, g) \leq \alpha
  \]

  Then, $\hk$ controls $\Err$ at $\alpha$
  whenever $p_{1:d}$ satisfy~\eqref{eq:indepCond_random_k0}.
\end{proposition}
\begin{proof}
  Fix any values $k_0\in \{0,\ldots,d, \infty\}$ and $q_{1:k_0} \in [0,1]^{k_0}$. We can construct a problem with $\tilde p_k \sim \delta_{q_k}$ for $k\leq k_0$ and  $\tilde p_k \sim \text{Unif}[0,1]$ for $k > k_0$. 
  \RTcomment{Will; what are the qk?  you mean we just choose and fix some values qk? Say so.} \WFcomment{Is it clearer now?}

  Then, for the fixed hypotheses 
  $\widetilde H_k:\; \tilde p_k \sim \text{Unif}[0,1]$, we have
  \[
  f(k_0, q_{1:k_0}) 
  = \E\left[ g\left(\hk(\tilde p_1, \ldots, \tilde p_d),
      k_0\right) \right],
  \]
  which is less than or equal to $\alpha$, since $\hk$ is assumed to control $\Err$ in the fixed-hypothesis case.

  But then, by the condition~\eqref{eq:indepCond_random_k0}, we have
  \begin{align}
    \Err(\hk,g) &\;=\; \E\left[ \;\E\left[ g\left(\hk(p_1,\ldots, p_d), k_0(Y)\right) \; \mid \; k_0(Y), \; p_{1:k_0}(Y)\right] \; \right]\\
    &\;\leq\; \E\left[f(k_0, p_{1:k_0})\right] \;\leq\; \alpha.
  \end{align}
\end{proof}

@@

Sections~\ref{sec:pValsIndep}--\ref{sec:SSP} discuss conditions on the model sequence $M_{0:d}$ and the $p$-value sequence $p_{1:d}$ under which~\eqref{eq:stochLargeCond_random_k0} is satisfied.

@@

Consider any filtration
\[
\sF_0 \sub \sF_1 \sub \cdots \sub \sF_d
\]
for which $M_{0:k}$ is measurable with respect to $\sF_k$. We say that $\sF_{0:d}$ {\em separates} the $p$-values $p_{1:d}$ if 
\begin{enumerate}
\item $p_k(Y)$ is conservative given $\sF_{k-1}$ 
  when $F\in M_{k-1}(Y)$, and
\item $p_k(Y)$ is measurable with respect to $\sF_k$.
\end{enumerate}
If $p_k$ is exact, the first requirement is equivalent to requiring that $p_k$ is independent of $\sF_{k-1}$ on the event $F\in M_{k-1}(Y)$ (i.e., the event when $p_k$ is null).

@@

  Let $p_{1:d}$ be selective $p$-values for $M_{0:d}$, 
  separated by $\sF_{0:d}$.

@@

We will concern ourselves mainly with the {\em sufficient filtration} for the path $M_{0:k}$, defined as
\[
\sF_k^{\text{suff}} = \sF(M_{0:k}, T_k),
\]
\RTcomment{Will- define $M_{0:k-1}$..  it is  the collection $\{ M_1 M_2 \ldots M_{k-1}\}$?} \WFcomment{I've now done so in Section~\ref{sec:notation}}.
We will suppress the superscript and use $\sF_k$ to mean $\sF_k^{\text{suff}}$ for the remainder of the article.

The sufficient filtration separates $p_{1:d}$ if and only if 
\begin{enumerate}
\item $p_k$ is conservative given $M_{0:k-1}$ and $T_{k-1}$, and
\item $p_k$ is a function of $M_{0:k}$ and $T_k$.
\end{enumerate}

To be a valid selective $p$-value for a single step, $p_k$ only needs to be conservative conditional on $M_{k-1}$. In general, it is more stringent to additionally require that $p_k$ must also condition on $T_{k-1}$ as well as the entire subpath $M_{0:k-1}$. In most cases of interest, however, the ``extra'' conditioning is redundant, for two reasons.

First, most selective tests already condition on $T_{k-1}$ in order to eliminate nuisance parameters. Second, as we will show in Section~\ref{sec:SSP}, for most path algorithms of interest we have
\begin{equation}\label{eq:SSP}
\sF(M_k, \, T_k) = \sF(M_{0:k}, \, T_k).
\end{equation}
Thus, most single-step selective $p$-values we would contemplate using are already exact conditional on $\sF_{k-1}$.

@@

We say that a path algorithm $M_{0:d}(\cdot)$ satisfies the {\em subpath sufficiency principle} (SSP) if~\eqref{eq:SSP} holds for every $k$. Equation~\eqref{eq:SSP} means that if we know $M_k(Y) = M$, then we can compute the entire subpath of models $M_{0:k}$ knowing only $T(Y, \, M)$, the sufficient statistic of model $M$. For example, given that four steps of forward stepwise linear regression yield the active set $E_4 = \{1,5,7,11\}$, the order in which these variables were included can be determined from $T_4 = X_{E_4}'Y$.

@@

Equation~\eqref{eq:onlyT} shows that $j_1,\ldots, j_{k-1}$ all depend on $Y$ only through $T_k(Y)$. As a result, it also follows that the enitre sequence $M_{0:k}(Y)$ depends only on $T_k(Y)$.
\end{proof}

@@

Collecting together the threads of this section, we can arrive at our main result: a fairly general sufficient condition for a $p$-value sequence to be independent on nulls.
\begin{theorem}[Sufficient Condition for Independence on Nulls] \label{thm:suffCond}
Assume that $T(Y; M)$ is a complete sufficient statistic for each candidate model $M$, that $p_k$ are exact selective $p$-values for $M_{k-1}$, and that $M_{0:d}(\cdot)$ satisfies the SSP.

If $p_k$ is $\sF_k$-measurable for each $k$, then the $p$-value sequence $p_{1:d}(Y)$ is independent on nulls.
\end{theorem}

\begin{proof}
We apply the definition of completeness to the function 
\[
h(T(Y; \, M)) \;=\; 
\P(p_k(Y) \leq \alpha \mid T(Y; \, M), \, M_{k-1}(Y) = M) - \alpha
\]
If $p_k$ is exact given $M_{k-1} = M$, then 
\[
\E_F[h(T_{k-1}) \mid M_{k-1}=M] \;=\; 0
\] 
for every $F\in M$. Therefore, we must have $h(T_{k-1})\eqAS 0$, so $p_k$ is independent of $\sF(M_k, T_{k-1})$. Because $M_{0:d}$ satisfies the SSP, $p_k$ is also independent of $\sF_{k-1} = \sF(M_{0:k-1}, T_{k-1})$.

If $p_k$ is also $\sF_k$-measurable, then the sufficient filtration separates $p_{1:d}$, implying that $p_{1:d}$ is independent on nulls.
\end{proof}

@@

If we follow this strategy, then the reference distribution for $U(Y)$ is measurable with respect to $T_{k-1}$ and $M_{k-1}$; moreover, if $U(Y)$ is also measurable with respect to $(M_k, T_k)$, the next model in the path and its sufficient statistics, then $p_k$ is measurable with respect to $\sF_k$, and so the $p$-value sequence $p_{1:d}$ will be independent on nulls per Theorem~\ref{thm:suffCond}.

@@

\begin{theorem}
  Assume the model path $M_{0:d}$ is obtained by forward stepwise 
  linear regression. Then, for a candidate active set $E$ of size $k$, 
  the set $A = \{E_k = E, \;X_E'Y = u\}$ is characterized 
  exactly by the constraints $X_E'Y=u$ and
  \[
  v_j^-(E,u) < X_j'Y < v_j^+(E,u), \quad\forall j \notin E,
  \]
  for $v_j^-$ and $v_j^+$ given explicitly in
  Equations~(\ref{eq:vMinus_FS}--\ref{eq:vPlus_FS}).
  Thus, $A$ corresponds exactly to 
  a set with $2(p-k)$ linear inequality constraints and $k$
  linear equality constraints on $Y$.
\end{theorem}

@@

\begin{theorem}
  Assume that $M_\infty$ is an exponential family model
  of the form
  \[
  Y \sim \exp\{ \theta'U(y) - \psi(\theta) \}\,d\nu(y),
  \]
  with $\Theta \sub \R^p$ convex, and assume
  that the model path $M_{0:d}$ is given 
  by the ever-active set for the $\ell_1$-penalized problem
  \begin{equation}\label{eq:regProblem}
  \hat\theta^r = \argmin_{\theta\in \Theta} 
  -\ell(\theta) + \lambda_r\|\theta\|_1,
  \end{equation}
  for some sequence $\lambda_r > 0$.

@@

\WFcomment{Should we compute the FWER and FDR only conditional on screening? Strong / Forward / Basic should all be correct given screening since they condition on $p_{1:k_0-1}$.}

@@

Essentially, we will want to partition the information in $Y$ according to the filtration:
\begin{align}\nonumber
  \sF(M_0,T_0) &\underlabel_{\text{selection } 1} 
  \sF(M_{0:1},T_0) \underlabel_{\text{inference } 1}
  \sF(M_{0:1},T_1) \quad \sub \;\;\cdots\\[8pt]
  \label{eq:infoPartition}
  \cdots\;\; \sub \quad&
  \sF(M_{0:d-1},T_{d-1}) \underlabel_{\text{selection } d}
  \sF(M_{0:d},T_{d-1}) 
  \underlabel_{\text{inference } d}
  \sF(M_{0:d}, T_d)
\end{align}

@@

\begin{comment}
\WFcomment{There is a filtration interpretation when you have the appropriate sufficiency properties.} Let $\sF_{k,i}$ denote the $\sigma$-algebra generated by $M_{0:k}$ and $p_{1:i}$.
\begin{align*}
  \sF_{k,i} &= \sF(M_{0:k},p_{1:i})\\
  \sF_0 &\underlabel_{\text{selection } 1} \sF_{1,0} \underlabel_{\text{inference } 1}
  \sF_{1,1} \;\;\sub \cdots \sub\;\;
  \sF_{d-1,d-1} \underlabel_{\text{selection } d} \sF_{d,d-1}
  \underlabel_{\text{inference } d} \sF_{d,d}
\end{align*}
\end{comment}
